---
title: "03-assignment: Trees"
author: "Christopher Brown"
date: "October 12, 2015"
output: html_document
---

## Readings

In Applied Predictive Modeling (APM) read:
- Chapter 8.1 - 8.8, 
- Chapter 11
- Chapter 14.1 - 14.5, 14.8

## Problems: Due October 26th, 2015 

- Project Update. (I will put a template in the projects folder for you to report your status on.) 

- Excersizes, In APM: 

8.1 (a) - (C)
8.4 (a) - (b)
14.2

```{r}
install.packages("mlbench")
library(mlbench)
set.seed(200)
simulated <- mlbench.friedman1(200,sd=1)
simulated <- cbind(simulated$x,simulated$y)
simulated <-as.data.frame(simulated)
colnames(simulated)[ncol(simulated)] <- "y"
install.packages("randomForest")
library(randomForest)
library(caret)
library(ggplot2)
library(lattice)
model1 <- randomForest(y~., data=simulated,importance= TRUE,ntree=1000)
rfImp1 <- varImp(model1,scale = FALSE)
simulated$duplicate1 <- simulated$V1 + rnorm(200)* .1
cor(simulated$duplicate1, simulated$V1)
model2 <- randomForest(simulated$duplicate1,simulated$V1,importance =TRUE,ntrees =1000)
install.packages("party")
library(party)
model2 <- cforest(y~.,data = simulated)
rfImp2 <-varimp(model2,conditional = FALSE)
rfImp2
```

```{r}
library(AppliedPredictiveModeling)
data(solubility)
trainingData <- solTrainXtrans
trainingData$Solubility <- solTrainY
LmFitALLPredictors <- lm (Solubility~MolWeight , data=trainingData)
summary(LmFitALLPredictors)
library(randomForest)
rfModel <- randomForest(solTrainXtrans,solTrainY,importance=TRUE,ntrees =1000)
summary(rfModel)
```


```{r}
install.packages("C50")
install.packages("ipred")
install.packages("gbm")
data(churn)

library(C50)
str(churnTrain)
table(churnTrain$class)
library(rpart)
library(ipred)
library(gbm)
fit1 <- rpart(churn~.,data = churnTrain)
fit2 <- bagging(churn~.,data = churnTrain)
fit3 <- gbm(churn~.,data=churnTrain,distribution = "gaussian")
install.packages("Cubist")
library(Cubist)
cubistMod <- train(churnTrain, churnTrain$churn,                                 data=churnTrain,method="cubist") 
liftCurve <- lift(churnTest$churn )                                   












