
---

title: "Resampling"
author: "Christopher Brown"
date: "October 5, 2015"
output: html_document
---


```{r}
set.seed(314159)
```


Use the `baseball` data set from the `plyr` package for the following problem.

A very simple model to predict the number of at-bats/game **each** player has per game is given by: 
 
     abpg = with(baseball,sum(ab)/sum(g) ) # 3.10
     

- Show that this is a bad:

```{r}
install.packages("plyr")
library(plyr)
library(gglot2)
ab
g
abpg
abpg = with(baseball,sum(ab)/sum(g) )
q_err <- quote(ab/g-abpg)
q_abpg <- quoto(sum(ab)/sum(g))
mean (eval(q_err,baseball),na.rm = TRUE)
hist(eval(q_err,baseball))
abpg = with(baseball,sum(ab)/sum(r))

```



- Create a better model using only number of games as a predictor

```{r}
attach(baseball)
fit <- lm(ab~g+0,baseball)
summary(fit)
any(g==0)
basebasll <- baseball[g!=0]
lm(ab~g+0)





```


- Calculate the "Apparent" *RMSE* of this model.    

```{r}
install.packages("hydroGOF")
install.packages("zoo")
install.packages("gglot2")
library(hydroGOF)
library(zoo)
library(plyr)
library(gglot2)
rmse(ab,g)
rmse <- function(error)
{
    sqrt(mean(error^2))
}
 

mae <- function(error)
{
    mean(abs(error))
}
 
error <- quote(ab/g-abpg)
rmse(error)
mae(error)
 
```


Using only Recreate the model, providing a new estimate for `ab/g` and the RMSE, using:
- 5-Fold CV
- Bootstrap

```{r}
library(caret)
attach(baseball)
set.seed(1)
cvSplits <- createFolds(fit,k=5,
                        returnTrain= TRUE)
str(cvSplits)
boot(cvSplits)


```

